Data Preparation

### 2021-06-29 x0_data-preparation.Rmd
initial thoughts on thresholds

>>>>

```{r}
#THRESHOLD AT A FIXED QUANTILE PER YEAR
ds1 <- full_dataset %>% group_by(YR = year(DATE), DATE) %>% summarize(N = n()) %>% mutate(THRESHOLD = quantile(N, probs = 0.7))
ds1

ds1 %>% ggplot(aes(x = DATE)) +
  geom_line(aes(y = THRESHOLD)) +
  geom_point(aes(y = N, color = N > THRESHOLD))

#CHECK WEEKLY DISTRIBUTION
ds2 <- ds1 %>% mutate(WEEK_DAY = wday(DATE, label = TRUE), W_END = WEEK_DAY %in% c("Sat", "Sun"))
ds2

ds2 %>% ggplot(aes(x = DATE)) +
  geom_line(aes(y = N, color = W_END))

ds2 %>% ggplot() +
  geom_freqpoly(aes(x = N, color = W_END))
```
